\documentclass[10pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\titleformat{\section}{\bfseries\Large}{}{0em}{}
\titleformat{\subsection}{\bfseries}{}{0em}{}
\titlespacing\subsection{0pt}{0pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\renewcommand\labelitemi{--}

\begin{document}

\begin{center}
    \textbf{\Large Devan L. O'Haro} \\
    \href{mailto:devanoharo@gmail.com}{devanoharo@gmail.com} · 443-386-2202 · \href{mailto:devan.l.oharo2.civ@us.navy.mil}{devan.l.oharo2.civ@us.navy.mil}
\end{center}

\section*{Summary}
U.S. Naval Nuclear Shift Test Engineer (STE) and U.S. Merchant Marine Academy graduate with extensive hands-on engineering experience in marine systems. Demonstrated leadership and expertise in technical writing, project coordination, and interdisciplinary collaboration. Seeking to leverage my technical background to contribute to innovative maritime and/or engineering solutions.

\section*{Work Experience}
\subsection{Nuclear Shift Test Engineer, Portsmouth Naval Shipyard \hfill 2019 -- Present}
\begin{itemize}[noitemsep]
    \item Planned, executed, and supervised nuclear submarine testing operations, ensuring quality and safety compliance.
    \item Authored detailed procedures and technical documents for S6G and S9G reactor testing and maintenance.
    \item Coordinated multi-disciplinary teams to meet operational deadlines and achieve performance milestones.
    \item Led process improvements, including the implementation of Git-based workflows for document management.
    \item Security Clearance: Active, Secret
\end{itemize}

\subsection{STEM Tutor \hfill 2022 -- Present}
\begin{itemize}[noitemsep]
    \item Conducted virtual and in-person sessions for middle school to college students primarily in Calculus I-III, Physics I-III, Chemistry I and II, and varying degrees of engineering/STEM subjects.
    \item Delivered personalized lesson plans to support conceptual understanding and academic success.
\end{itemize}

\subsection{Engine Cadet, Various Vessels \hfill 2015 -- 2016}
\begin{itemize}[noitemsep]
    \item Performed daily system maintenance and operational tasks aboard vessels including \textit{ARC Endurance}, \textit{USNS Zeus}, \textit{USS Montpelier} (submarine)  and \textit{Philadelphia Express}.
    \item Completed technical sea projects demonstrating mastery of marine systems and propulsion operations.
    \item Completed system start-up and shut-down operations.
    \item Stood watch and logged system maintenance and disseminated repair action plans to licensed duty engineers.
\end{itemize}

\subsection{Midshipman Company Commander, U.S. Naval Reserves \hfill 2014 -- 2019}
\begin{itemize}[noitemsep]
    \item Selected and served as Company Commander. Led 100+ underclass midshipman by carrying out regiment and academy direction. Enforced midshipman regulations, executed the plan of the day, oversaw barrack maintenance and cleanliness, held company and individuals accountable and executed good order and discipline actions when needed.
\end{itemize}

\subsection{Assistant Manager, GameStop \hfill 2013 -- 2014}
\begin{itemize}[noitemsep]
    \item Managed inventory, staff scheduling, and store operations to ensure efficient workflows.
\end{itemize}

\section*{Skills}
\textbf{Technical:} Microsoft Office, Java, C++, Python, GNU/Linux, LATEX, network processes \\
\textbf{Industrial:} Welding, metal fabrication, plumbing, electrical work, SOLAS safety protocols \\
\textbf{Leadership:} Coordination of teams at Portsmouth Naval Shipyard; Company Commander during time at USMMA \\

\newpage

\section*{Projects}
\subsection{Submarine Maintenance and Testing}  
\begin{itemize}[noitemsep]
    \item \textit{USS Santa Fe}: Assisted in Depot Maintenance Period preparation, executing complex system line-ups for successful operations.
    \item \textit{USS California}: Acted as STE during an abbreviated Depot Maintenance Period, leading key evolutions.
    \item \textit{USS Texas}: Directed testing and nuclear maintenance operations as a qualified STE for a Virginia-class submarine (S9G plant).
    \item \textit{USS Virginia}: Planned and coordinated critical operations, ensuring adherence to performance and safety standards.
    \item \textit{USS Asheville}: Authored procedures for secondary systems testing and maintenance to streamline project goals.
\end{itemize}

\subsection{Independent Study: Convection-Diffusion Modeling}  
\begin{itemize}[noitemsep]
    \item Conducted computational modeling of convection-diffusion equations using high-order matrices to simulate cell movement through scaffolds in fluid dynamics.
\end{itemize}

\subsection{Process Improvement Initiative}  
\begin{itemize}[noitemsep]
    \item Led the integration of Git-based workflows to enhance team collaboration in technical documentation development.
\end{itemize}

\subsection{Fabrication Precision for Maritime Applications}  
\begin{itemize}[noitemsep]
    \item Designed and fabricated custom metal components with tolerances down to one-thousandth of an inch for integration into maritime systems.
\end{itemize}

\section*{Education}

\subsection{B.S. Marine Engineering Systems, United States Merchant Marine Academy \hfill June 2019}
\textit{Graduated Cum Laude}, GPA: 3.65 \\
\textbf{Certificates:} U.S. Coast Guard Unlimited Horsepower Third Assistant Engineer’s License (Diesel, Gas Turbine, Steam) \\
\textbf{Relevant Courses:} Marine Engineering, Thermodynamics, Naval Architecture, AI Introduction, Cryptology, Machine Elements, Fluid Dynamics\\

\subsection{Shift Test Engineer Certification, Portsmouth Naval Shipyard \hfill August 2022}
Comprehensive 3-year training program in nuclear submarine reactor systems (S6G/S9G reactors). Licensed to manage and assist operations.\\

\subsection{Fundamentals of Engineering (Other Disciplines) \hfill July 2019}
First milestone toward Professional Engineer (PE) licensure.

\section*{Extracurricular Activities}
Cyber-Defense-Club (President), Computer Building, Regimental Band, Club Ice Hockey, 3-D Printing Club, Auto Club, Chess Club (President), SCUBA Diving open-water certified, O’Gara Academic Honors Society, off-shore sailing team.

\section*{Personal}
Ambition to advance skills in 3D modeling and data science through MIT xPRO programs. \\
Interests include SCUBA diving, woodworking, chess, hockey, skiing, and programming.

\end{document}
